Creating Named Valleys Dataset

### 2023-11-15 manuscript/manuscript_APPS.rmd
forgot to ignore .zip
working on

```{r load in time trials}
time_trials <- readRDS('data/processed/time_trials')
tt_local <- time_trials[time_trials$Group=='Local',]
```

It took roughly *six* minutes (`r sum( time_trials[time_trials$Group=='Local', 'elapsed'])`s) to run all local steps of BarnebyLives, and roughly 20 minutes (`r time_trials[time_trials$Function=='powo_searcher', 'elapsed']`s) to search Plants of the World Online, and `r time_trials[time_trials$Function=='directions_grabber', 'elapsed']` to search Google Maps and write directions to sites.
Most of the local run time is attributable to the spatial (spatial: `r sum(tt_local[tt_local$Module=='Geospatial', 'elapsed'])`s), and taxonomic operations (`r sum(tt_local[tt_local$Module=='Taxonomic', 'elapsed'])`), style: `r sum(tt_local[tt_local$Module=='Style', 'elapsed'])`. 
The spell check operation of the scientific name accounted for nearly all of the time (`r sum(tt_local[tt_local$Function=='spell_check', 'elapsed'])`) spent performing local taxonomic operations.
The generation of labels consumed around XX minutes for the rendering, XX to combine individual labels four per single sheet of landscape orientated paper, and XX to combine the XX sheets to a single Portable Document Format (PDF).

@@

data_p %>% 
  filter(Binomial_authority != POW_Name_authority)

>>>>

```{r load in time trials}
time_trials <- readRDS('data/processed/time_trials')
tt_local <- time_trials[time_trials$Group=='Local',]
time_label_gen <- readRDS('../data/processed/time_label_gen')
```

```{sh, count number of files in directory}
cd labels/processed
ls -1 | wc -l
```

It took roughly *six* minutes (`r sum( time_trials[time_trials$Group=='Local', 'elapsed'])`s) to run all local steps of BarnebyLives, and roughly 20 minutes (`r time_trials[time_trials$Function=='powo_searcher', 'elapsed']`s) to search Plants of the World Online, and `r time_trials[time_trials$Function=='directions_grabber', 'elapsed']` to search Google Maps and write directions to sites.
Most of the local run time is attributable to the spatial (spatial: `r sum(tt_local[tt_local$Module=='Geospatial', 'elapsed'])`s), and taxonomic operations (`r sum(tt_local[tt_local$Module=='Taxonomic', 'elapsed'])`), style: `r sum(tt_local[tt_local$Module=='Style', 'elapsed'])`. 
The spell check operation of the scientific name accounted for nearly all of the time (`r sum(tt_local[tt_local$Function=='spell_check', 'elapsed'])`) spent performing local taxonomic operations.
The generation of labels consumed around `r time_label_gen` minutes for the rendering, XX to combine individual labels four per single sheet of landscape orientated paper, and XX to combine the XX sheets to a single Portable Document Format (PDF).

@@

#data_p %>% 
#  filter(Binomial_authority != POW_Name_authority)

### 2023-11-15 scripts/valleys_create.Rmd
working on

states <- tigris::states() %>% 
  filter(NAME %in% c('California', 'Nevada', 'Utah', 
                     'Arizona', 'New Mexico', 'Colorado', 'Idaho', 'Washington', 'Oregon')) %>% 
  select(NAME)

out <- st_intersection(output1, states)
out <- select(out, -NAME)

@@

st_write(gnis_sub, '../ValleysProject/data/places/places.shp')
st_write(out, '../ValleysProject/data/valleys/valleys.shp', append = F)
```

>>>>

# states1 <- tigris::states() %>% 
#  filter(NAME %in% c('California', 'Nevada', 'Utah', 
#                     'Arizona', 'New Mexico', 'Colorado', 'Idaho', 'Washington', 'Oregon')) %>% 
#  select(NAME)

#out <- st_intersection(output1, states)
# out <- select(out, -NAME)

states1 <- tigris::states() %>% 
  filter(NAME %in% c('Montana', 'Wyoming', 'Texas', 'Oklahoma', 'South Dakota', 'North Dakota', 'Kansas')) %>% 
  select(NAME)

out <- st_intersection(output1, states1)
out <- select(out, -NAME)

@@

st_write(gnis_sub, '../ValleysProject/data/places/places.shp')

# st_write(out, '../ValleysProject/data/valleys/valleys.shp', append = F)
st_write(out, '../ValleysProject/data/valleys/valleys-heartland.shp', append = F)
```
